%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{AHMED ELNAMOURY} \\[7.5pt]
\href{https://github.com/username}{\raisebox{-0.05\height}\faGithub\ MIVIDA EMAAR, New Cairo, Egypt 11865} \ $|$ \ 
\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ aelnamoury@petrobel.org} \ $|$ \ 
\href{mailto:email@mysite.com}{\raisebox{-0.05\height}\faEnvelope \ engnmero@gmail.com} \ $|$ \ 
\href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +971-586749290/ +20-1007336555} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Objective}
Field Operations Management Professionalism in Oil & Gas Fields using critical thinking and communication/teamwork skills plus the ability to work independently. Seeking a challenging assignment with an opportunity for growth and career advancement in a dynamic international organization in the field of   Production   Operations and   Assets   Integrity   &   Reliability Management.
My motivation is to be the best in everything that I do no matter how simple that thing is to help myself by helping others.  I really enjoy and am very keen on optimizing all operations activities, and solving complex technical problems).

%Interests/ Keywords/ Summary
\section{Professional Summary}
Department manager of Process & operation Division with fourteen years’ experience in ABU MADI field (14% of Egypt gas production about 970 MMSCFD. In which have two off shore platforms and onshore gas wells connected by piping networks to onshore treatment plants (4 Raw gas TURBO-COMP, 6 LTS Trains, 2NGL plants, and Shipping area).

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Currently Working as Department manager of Process & operation Division  at PETROBEL/ENI JV (ABU MADI FIELD } & \hfill Jan 2021 - present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{ Perform tech service functions relating to day to day process, project problem-solving
 Arrangements with maintenance teams through CMMS 
 making inspection tour through all plants for verification HSE complying, and developing IMMS.   
 issuing production allocation daily, monthly, and annually reports between share holders (ENI&BB&TOTAL&EGPC) 
 Perform on job training for junior engineers in team for readiness through daily activities to put them in situational phases (instructions/coaching/ monitor controlling/ delegation)
 Process engineering functions through my team encompass monitoring the unit performance, modeling unit operation, optimizing unit efficiency, originating operating procedures, and troubleshooting unit problems.
 Project engineering functions encompass conceiving, justifying, designing, and implementing projects for improving process efficiency, increasing products recovery, and complying with HSE.
 Support turnaround planning, associated shutdown activities as well as MOC’s HAZOP reviews, and associated follow-up actions.
}  \\
\end{tabularx}

%Projects
\section{Achievements}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{ Increasing LPG production by about 15 tons /day in NGL plant by optimizing the operating condition through using aspen HYSIS dynamic.
 Maximizing trunk lines networks capacities by about 7% between off shore platforms and treatment plants by PIPSIM software. 
 Fuel gas consumption optimization.
 Adjust mode of operation for upgrading Turbo-Compressors through life phases for gas wells.
 Engineering MOCS to eliminate risks and increasing profits in all plants. 
 Design python program for liquid shipping products (condensate &LPG) calculation.
 Survive low potential gas wells during facilities S/D by installing some minor modification(MOC’s).
 Engineering study for degassing system for waste water API tank to reduce environment impact.
}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	

2002 - 2007 & Bachelor's Degree at \textbf{Chemical Engineering and Petroleum Refinery Faculty of Petroleum Engineering, Suez Canal University.} \\ 

\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Courses & Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
	Simulation software (ASPEN HYSIS, PIPSIM, OLGA FLOW ASSURANCE)
	Analytical/Problem solving
	Data analysis
	Economics Feasibility studies
	Project management
	Teamwork and collaboration 
	Effective communication 
	Acute decision making
	Leadership
	Fluent in English and Arabic
\\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
